The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-30 ms.Rmd
Suppress message output and hide responsecurve figures.

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/')

@@

```{r fengChangeWorkflow, eval = TRUE}
Feng_Papes_interactive <- ChangeWorkflow(
    Feng_Papes,
    output = Chain(PerformanceMeasures, PrintMap, InteractiveMap, ResponseCurve))
```

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/', message = FALSE)

@@

```{r fengChangeWorkflow, eval = TRUE, fig.show = 'hide'}
Feng_Papes_interactive <- ChangeWorkflow(
    Feng_Papes,
    output = Chain(PerformanceMeasures, PrintMap, InteractiveMap, ResponseCurve))
```
